---
title: "Egypy Cell Towers"
author: "Hany Nagaty"
output:
  pdf_document: default
  html_notebook: default
---

I came across the [OpenCelliD](https://opencellid.org) web site that has a database for all the cell sites in the globe. I downloaded the data for Egypt, all 4 operators, and I’m presenting them here.

Just mind the license that states that “*Data is free to use & distribute. We only ask that you include the following attribution string visibly.*”

***[OpenCelliD Project](https://opencellid.org/) is licensed under a [Creative Commons Attribution-ShareAlike 4.0 International License](https://creativecommons.org/licenses/by-sa/4.0/)*** 

### Useful Links
+ This link has a description for the data http://wiki.opencellid.org/wiki/Menu_map_view#Cells_database

+ This is a useful FAQ http://wiki.opencellid.org/wiki/FAQ


```{r include=FALSE}
library(tidyverse)
library(janitor)
library(lubridate)
library(knitr)
```


```{r readData, include=FALSE}
cell_towers <- read_csv(
  "~/dataLocal/cellTowers/cell_towers.csv",
  col_type = cols(
    radio = col_factor(),
    mcc = col_double(),
    net = col_double(),
    area = col_double(),
    cell = col_double(),
    unit = col_double(),
    lon = col_double(),
    lat = col_double(),
    range = col_double(),
    samples = col_double(),
    changeable = col_double(),
    created = col_double(),
    updated = col_double(),
    averageSignal = col_double())
)

egypt <- cell_towers %>% 
  filter(mcc == 602) %>% 
  mutate(created = as.POSIXct(created, origin="1970-01-01"),
         updated = as.POSIXct(updated, origin="1970-01-01")) %>% 
  mutate(created_date = as.Date(created),
         created_week = floor_date(created, unit = "week"),
         created_month = floor_date(created, unit = "month"))
```

### Summary Table
```{r table, echo=FALSE, message=FALSE, warning=FALSE}
egypt %>% 
  mutate(radio = fct_drop(radio)) %>% 
  rename("Network" = "net") %>% 
  tabyl(Network, radio) %>% 
  adorn_percentages("row") %>%
  adorn_pct_formatting(digits = 2) %>% 
  adorn_ns() %>% 
  kable()
```

### Time Plot
```{r plot, echo=FALSE, message=FALSE, warning=FALSE}
egypt %>% 
  mutate(radio = fct_drop(radio)) %>% 
  rename("Network" = "net") %>% 
  group_by(created_week, Network, radio) %>% 
  count() %>% 
  ungroup(created_week) %>% 
  mutate(cells = cumsum(n)) %>% 
  ggplot(aes(x = created_week, y = cells, col = radio)) +
  geom_line() +
  facet_wrap(vars(Network), labeller = "label_both")
```

